Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Ensmallen extension diagram.
grammar fix

\paragraph{TCP payload length}
Figure \ref{fig:len} shows the payload size distribution of normal Google traffic and meek traffic. Both
figures exhibit a significant amount of packets with no payload. These packets are mostly TCP SYN and ACK
packets. Figure \ref{fig:len:lbl} shows the distribution of normal traffic, which indicates a large portion
of small-sized packets. However, in the meek traffic shown in Figure \ref{fig:len:meek}, most packets
are large packets ranging from 1400 bytes to 1500 bytes. This result is unexpected, because the underlying packets 
in the TLS session are sent from Tor. By default, each Tor cell is 512 bytes, but meek changes the packet size 
distribution. Therefore, meek provides traffic shaping without additional efforts.

To explain the phenomenon, recall that we use browsers to handle HTTPS connections for meek in order
to hide TLS handshake characteristics.
Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the meek trace.
In contract, normal users may not have persistent connections to Google. For example, a user may search a keyword on
Google, click a result, and then close the tab that displays search results. The browser may close the 
connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
opens a new connection. In this case, small requests do not have such opportunity for batching.

@@

The distribution of meek traffic, in contrast, is totally different. First, there are much fewer connections, which is 
consistent with the discussions above. Second, the durations are much longer if we notice the x-axis in Figure \ref{fig:duration:meek}. If there is not a case in which normal users also have such long connections when browsing Google, the 
censor can potentially block any long connections between users and Google. Even if this is the case, the
censor has to wait until a time threshold is reached. The user might have already obtained the forbidden data she wants, or 
meek could simply restart a connection.

\paragraph{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
distinguishing the meek traffic. But admittedly there two potential weaknesses: long-lived connections 
with bulk data transfer, and deviated distribution of packet sizes. To fundamentally fix these weaknesses 
we need to transform to the traffic into the normal-looking traffic. The problem is inherently difficult, because we need to know \emph{what} is normal traffic, i.e. what is the model of normal traffic, which is an open problem. However, 
the arm-race game is symmetric; since finding a right model is a difficult task for us, it is also difficult for 
the censor. Therefore, the censor can only find ad-hoc features to block forbidden traffic, which are relatively 
easy to defend against.

>>>>

\paragraph{TCP payload length}
Figure \ref{fig:len} shows the payload size distribution of normal traffic and meek's traffic. Both
figures exhibit a significant amount of packets with no payload. These packets are mostly TCP SYN and ACK
packets. Figure \ref{fig:len:lbl} shows the distribution of normal traffic, which indicates a large portion
of small-sized packets. However, in the meek's traffic shown in Figure \ref{fig:len:meek}, most packets
are large packets ranging from 1400 bytes to 1500 bytes. This result is unexpected, because the underlying packets 
in the TLS session are sent from Tor. By default, each Tor cell is 512 bytes, but meek changes the packet size 
distribution. Therefore, meek provides traffic shaping without additional efforts.

To explain the phenomenon, recall that we use browsers to handle HTTPS connections for meek in order
to hide TLS handshake characteristics.
Browsers also apply techniques like HTTP pipelining to improve performance. Since meek is always communicating with
the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
records meek's traffic.
In contract, normal users may not have persistent connections to Google. For example, a user may search a keyword on
Google, click a result, and then close the tab that displays search results. The browser may close the 
connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
opens a new connection. In this case, small requests do not have such opportunity for batching.

@@

The distribution of meek's traffic, in contrast, is totally different. First, there are much fewer connections, which is 
consistent with the discussions above. Second, the durations are much longer if we notice the x-axis in Figure \ref{fig:duration:meek}. If there is not a case in which normal users also have such long connections when browsing Google, the 
censor can potentially block any long connections between users and Google. Even if this is the case, the
censor has to wait until a time threshold is reached. The user might have already obtained the forbidden data she wants, or 
meek could simply restart a connection.

\paragraph{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
distinguishing meek's traffic. But admittedly there two potential weaknesses: long-lived connections 
with bulk data transfer, and deviated distribution of packet sizes. To fundamentally fix these weaknesses 
we need to transform to the traffic into the normal-looking traffic. The problem is inherently difficult, because we need to know \emph{what} is normal traffic, i.e. what is the model of normal traffic, which is an open problem. However, 
the arm-race game is symmetric; since finding a right model is a difficult task for us, it is also difficult for 
the censor. Therefore, the censor can only find ad-hoc features to block forbidden traffic, which are relatively 
easy to defend against.
